Repeatability Test

### 2017-07-04 pt_characterization/rep_check/u_s_time.tex
3d plot generation

\section{Further invstigation of the Second Run~\label{sec:u_s_time_hist}} 
This section exhibits user and system time histograms on the second run of 
INC with its task length increasing from 1 second to 4096 seconds. 
The detailed description of the base data is from Table~\ref{tab:exp_notes2}, 
and for some additional data, the corresponding description is given in Table~\ref{tab:exp_notes3}.

>>>>

\section{Further investigation of the Second Run~\label{sec:u_s_time_hist}} 
This section exhibits user and system time histograms on the second run of 
INC with its task length increasing from 1 second to 4096 seconds. 
The detailed description of the base data is from Table~\ref{tab:exp_notes2}, 
and for some additional data, the corresponding description is given in Table~\ref{tab:exp_notes3}.
